



```{r}
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("clusterProfiler")
```

```{r}
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("AnnotationDbi", force = TRUE)
```

```{r}
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("org.Ce.eg.db", force = TRUE)
```

```{r}
library(clusterProfiler)
library(org.Ce.eg.db)
library(AnnotationDbi)
```

```{r}
sg_symbols <- read.csv('sg_symbols.csv', header = FALSE)

genes_to_test <- sg_symbols$V2
```


ont can be BP, CC, MF
biological process, cellular component, molecular function
```{r}
GO_results <- enrichGO(gene = genes_to_test, 
                       OrgDb = 'org.Ce.eg.db', 
                       keyType = 'SYMBOL',
                       ont = 'BP')
```
BP background is 9826
CC background is 12602
MF background is 9895


why are there to few genes in the background
in the python version, got 19983 genes
but background is different for each type of ont
something about universe, see:
if universe is missing, all genes in database will be used as background
clusterprofiler does some filtering automatically
```{r}
as.data.frame(GO_results)
```
dev.off issue fix:
https://www.reddit.com/r/RStudio/comments/1hsd1w7/frustrating_issue_with_saving_pngs_of_plots_in_r/
```{r}
fit <- plot(barplot(GO_results, showCategory = 20))

png('/home/carl/Code/isoforms/APCanalysis/go/go_out.png', 
    res = 250, width = 1200, height = 2000)
#dev.off()
dev.off(dev.list()["png"])

fit
```








